Measurement and Analysis of Child Pornography Trafficking on P2P Networks\nocite{Hurley}

### 2013-10-14 Paper_presentation.tex
Table 3
Parte do Mestre finalizada e Agenda

@@

\begin{frame}
\begin{block}{We can see this  result under the table:}

@@

\begin{tabular}{ccc}

@@

\hline
\end{tabular}
\label{table2}
\end{table}

@@

>>>>

\AtBeginSection[]{%
  \begin{frame}
    \frametitle{Schedule}
    \tableofcontents[currentsection]
  \end{frame}
  \addtocounter{framenumber}{-1}% If you don't want them to affect the slide number
}

@@

\begin{frame}
\begin{block}{We can see this result under the tables:}

@@

\begin{tabular}{ccc}\hline & \multicolumn{2}{c}{Network} \\

@@

\hline
\end{tabular}
\label{table2}

\end{table}

@@

\begin{block}

\caption{Numbers of IP addresses per network sharing FOI}

\begin{tabular}{cccc}\hline & \multicolumn{3}{c}{IP Adresses} \\

Network & Total & Private & TOR \\

\hline
\hline
Gnutella & 3,025,530 & 32,195 & 7,357 \\
eMule & 5,643,350 & 1,256 & 21,025 \\
Ares & 1,714,894 & 225 & 1,799 \\
IRC & 88,658 & 245 & 746 \\

\end{tabular}
\label{table3}

\end{table}

\item[\checkmark]The differences of each subgroup to the set of all GUIDs are significant (p < 0.001).

\item[\checkmark]Below we provide characteristics of each subgroup, and details of the behavior of each.

\item[\checkmark]For example, we show that GUIDs using TOR to share FOI use it irregularly, and therefore their true IP addresses are easily identifiable.
